Output Summary

### 2021-10-11 03-post-process/output-plots.Rmd

# extract the two key structures from this object
post = model_info$post
# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data
```

```{r dimension-ids}
# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny

# population names
pops = colnames(jags_data$Ra_obs)

@@

```{r vcov-decomp, message = FALSE}
# Convert the precision matrices monitored by JAGS into the marginal SD and correlation matrix terms
# postpack::vcov_decomp() does this for all posterior samples

Sig_Lphi_O0_O1_post = suppressMessages(vcov_decomp(post, "Sig_Lphi_O0_O1", invert = FALSE, sigma_base_name = "sig_Lphi_O0_O1", rho_base_name = "rho_Lphi_O0_O1"))

# make the labels/indices for which elements of the vcov matrices contain unique covariances
# no point in summarizing/displaying both off-diagonal triangles
dummy_cols = matrix(rep(1:jags_data$nj, each = jags_data$nj), jags_data$nj, jags_data$nj)
dummy_rows = matrix(rep(1:jags_data$nj, jags_data$nj), jags_data$nj, jags_data$nj)
vcov_cols = dummy_cols[lower.tri(dummy_cols)]
vcov_rows = dummy_rows[lower.tri(dummy_rows)]
vcov_labels = paste0(pops[vcov_rows], "-", pops[vcov_cols])
vcov_indices = paste0("[", vcov_rows, ",", vcov_cols, "]")

# subset out only the unique elements
Sig_Lphi_O0_O1_post = post_subset(Sig_Lphi_O0_O1_post, c("sig", paste0("rho.+", vcov_indices)))

# combine these derived posterior samples with the main object
post = post_bind(post, Sig_Lphi_O0_O1_post)
```

@@

# Year 1 ocean survival
L1 = "Year 1 Ocean Survival"
L2 = c("Mean", "Process SD", "Among Pop. Correlation", "Realized")
base = c("mu_phi_O0_O1[origin,pop]", "sig_Lphi_O0_O1[pop]", "rho_Lphi_O0_O1", "phi_O0_O1[year,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
phi_O0_O1_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Year 2 ocean survival
L1 = "Year 2 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O1_O2[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
phi_O1_O2_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Year 3 ocean survival
L1 = "Year 3 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O2_O3[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
phi_O2_O3_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
base = c("O_phi_scaler_nat_hat[pop]", "Lphi_O0_O1_resid[5,1,pop]", "kappa_phi_O0_O1[pop]")
match = sub_index(base, pop = ".")
misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  omega_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_O2_O3_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

## Smolt-to-Adult Rates {.tabset .tabset-pills}

### LGR to Tributary

@@

### BON to BON

```{r bon-to-bon, fig.width = 6, fig.height = 5}
sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]

  # summarize rates
  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = j))
  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_hor, pop = j))

  # get a max value for ylim
  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = "."))["97.5%",])

  # make hatchery values NA in year with no smolt
  phi_hor[,zero_hor_smolt] = NA

  # plot natural origin time series
  plot_tseries(est = phi_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, ymax))

  # add hatchery origin time series
  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(phi_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
  lines(phi_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
  lines(phi_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)

  if (j == 1) {
    legend("topright", legend = c("NOR", "HOR"), title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
```

@@

# Ocean Survival {.tabset .tabset-pills}

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
ocean_surv_plot = function(j) {
  par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_nor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O0_O1[.+,origin,pop]", origin = o_hor, pop = j)),
               main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_nor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O1_O2[.+,origin,pop]", origin = o_hor, pop = j)),
               main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_nor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^phi_O2_O3[.+,origin,pop]", origin = o_hor, pop = j)),
               main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = all_yrs[observable], ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.5, "Brood Year")
  mtext(side = 2, outer = T, line = 0, "Survival")
}
```

```{r}
ocean_surv_plot(j_cat)
```

```{r}
ocean_surv_plot(j_los)
```

```{r}
ocean_surv_plot(j_min)
```

```{r}
ocean_surv_plot(j_ugr)
```

>>>>

# extract the two key structures from this object
post = model_info$post
# post = post_thin(model_info$post, keep_percent = 0.1)  # uncomment this to run document with 10% of the retained MCMC samples
jags_data = model_info$jags_data

# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny
```

```{r dimension-ids}
# population names
pops = colnames(jags_data$Ra_obs)

@@

@@

# Year 1 ocean survival
L1 = "Year 1 Ocean Survival"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_O0_O1[origin]", "sig_Lphi_O0_O1", "phi_O0_O1[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
phi_O0_O1_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Year 2 ocean survival
L1 = "Year 2 Ocean Survival"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_phi_O1_O2[origin]", "sig_Lphi_O1_O2", "phi_O1_O2[year,origin]")
match = sub_index(base, year = ".+", origin = o_nor)
phi_O1_O2_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# Misc ocean survival
L1 = "Misc Ocean Survival"
L2 = c("NOR:HOR Scaler", "Year 0 Residual", "AR(1) Coefficient")
match = c("O_phi_scaler_nat_hat", "Lphi_O0_O1_resid[5]", "kappa_phi_O0_O1")
misc_ocean_surv_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  omega_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

## Smolt-to-Adult Rates

@@

@@

# Ocean Survival

```{r ocean-surv-plots, fig.width = 6, fig.height = 5}
par(mfrow = c(3,2), oma = c(1.5,1.5,0,0))
plot_tseries(post_summ(post, "phi_O0_O1[.+,1]$"), main = TeX("$O_0 \\rightarrow O_1\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O0_O1[.+,2]$"), main = TeX("$O_0 \\rightarrow O_1\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,1]$"), main = TeX("$O_1 \\rightarrow O_2\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O1_O2[.+,2]$"), main = TeX("$O_1 \\rightarrow O_2\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,1]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(NOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
plot_tseries(post_summ(post, "phi_O2_O3[.+,2]$")[,2:(length(observable)+1)], main = TeX("$O_2 \\rightarrow O_3\\,(HOR)$"), yrs = as.numeric(rownames(jags_data$Pa_obs)[observable]), ylim = c(0,1))
mtext(side = 1, outer = T, line = 0.5, "Brood Year")
mtext(side = 2, outer = T, line = 0, "Survival")
```
